### 2021-07-22 doc/thesis/chapters/hls.tex
code formatting

The following code example shows the specification of an AXI4-Lite memory-mapped slave interface.
The provided registers are separated into config registers and status registers.
The config is readable and writeable, while the status registers are implemented as read-only, which requires less logic in the RTL implementation.\\

\begin{program}
  \caption{Implementation of an AXI4-Lite memory-mapped slave with read-only and read-write registers.}
  \label{prog:axi4_lite}
  \begin{CppCode}
    typedef struct {
      ap_int<NUM_LEDS> led_ctrl;
      uint8_t code;
    } config_t;

@@

Another code example demonstrates the equally simple definition of an AXI4-Stream interface.

\begin{CppCode}
  #include <hls_stream.h>

  void hls_ip_top_level(hls::stream<uint32_t>& sample_in,
                        hls::stream<uint32_t>& audio_out) {
      #pragma HLS INTERFACE axis port = sample_in
      #pragma HLS INTERFACE axis port = audio_out
  }
\end{CppCode}

>>>>

The program code example \ref{prog:axi4_lite} shows the specification of an AXI4-Lite memory-mapped slave interface.
The provided registers are separated into configuration registers and status registers.
The configuration is readable and writeable, while the status registers are implemented as read-only, which requires less logic in the RTL implementation.\\

\begin{program}
  \caption{Implementation of an AXI4-Lite memory-mapped slave with a separation of read-only status registers and read-write configuration registers.}
  \label{prog:axi4_lite}
\begin{CppCode}
 typedef struct {
   ap_int<NUM_LEDS> led_ctrl;
   uint8_t code;
 } config_t;

@@

The second program code example \ref{prog:axi4_stream} demonstrates the equally simple definition of an AXI4-Stream interface.

\begin{program}
  \caption{Implementation of an AXI4-Stream interface.}
  \label{prog:axi4_stream}
\begin{CppCode}
 #include <hls_stream.h>

 void hls_ip_top_level(hls::stream<uint32_t>& sample_in,
                       hls::stream<uint32_t>& audio_out) {
     #pragma HLS INTERFACE axis port = sample_in
     #pragma HLS INTERFACE axis port = audio_out

     ...
 }
\end{CppCode}
\end{program}
